---
title: "Final Project for Pratical Machine learning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Soroush Rasti
##### March 2020

At first, the neceeary libraries and the input data are imported:

```{r 1}
library(caret)
data<-read.csv('pml-training.csv')
testing_final<-read.csv('pml-testing.csv')
```

After that, the data are cleaned and the coloums with 'NAN' values are deleted:

```{r 2}
data <- data[,colSums(is.na(data))==0]
testing_final <- testing_final[,colSums(is.na(testing_final))==0]
```
It seems that the first six coloums are also needed to removed since they only have dates and times information which is not usefull for the modeling of this work.

```{r 3}
data <- data[,-c(1:6)]
testing_final <- testing_final[,-c(1:6)]
```

Finnaly the cleaned data seems like this:

```{r 3-1}
str(data[,1:10])
```

Since the cross validation analysis shoule be done withing the testing_final dataset, another testing data for measuring accuracy is derived by caret package based on the distrubution of Class varibale:

```{r 4}
tr <- createDataPartition(y=data$classe, p=0.7, list=FALSE )
training <- data[tr,]
testing <- data[-tr,]
```

In below, the training data is used for modeling through RANDOM FOREST method. Afterwards, the prediction and accuracy are calculated according to the testing data.

```{r 5 ,eval=F, echo=T}
model <- train( classe~ ., data=training, method='rf')
initial_prediction <- predict(model, testing)
confusionMatrix(initial_prediction, testing$classe)
```

The accuracy is  0.90 . The same model predicts the 20 cases of the testing_final as below: 


```{r 6,eval=F, echo=T}
predict(model, testing_final)
```


Here, another model, 'gbm' is used to calculate the accuracy and do prediction:
```{r 7,eval=F, echo=T}
model <- train( classe~ ., data=training, method='gbm')
initial_prediction <- predict(model, testing)
confusionMatrix(initial_prediction, testing$classe)
```

So, the accuracy is  0.89 . The same model predicts the 20 cases of the testing_final as below: 


```{r 8,eval=F, echo=T}
predict(model, testing_final)
```